---
title: "ggplot2movies exploration"
output: html_document
---

See [ggplot2movies.pdf](https://cran.r-project.org/web/packages/ggplot2movies/ggplot2movies.pdf) for details on the ggplot2movies package

# Goal

I'd like to see what insights this data set can give into movie profit. For example:
  How due different genre's profits compare 
  How does rating correlate with profit
  What are the trends in rating or votes over the course of time and/or genre 
  
## Note
Here are some of the types of analysis I might want to do here:

- Descriptive analysis (to summarize the data set)  
- Exploratory analysis (to identify relationships not causes)  
- Inferential analysis  
- Predictive analysis  
- Causal analysis
- Mechanistic analysis

# Prepare Environment
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require("pacman")) install.packages("pacman")
```

```{r}
pacman::p_load(ggplot2movies, dplyr)
movies <- ggplot2movies::movies
```

# Describe the Data

# Data Cleaning

# Explore the Data
```{r, Genre Dataframes}

movies_action <- movies %>% 
  filter(movies$Action == 1) %>% 
  select(title, year, length, budget, rating, votes)

movies_animation <- movies %>% 
  filter(movies$Animation == 1) %>% 
  select(title, year, length, budget, rating, votes) 

movies_comedy <- movies %>% 
  filter(movies$Comedy == 1) %>% 
  select(title, year, length, budget, rating, votes) 

movies_drama <- movies %>% 
  filter(movies$Drama == 1) %>% 
  select(title, year, length, budget, rating, votes)

movies_documentary <- movies %>% 
  filter(movies$Documentary == 1) %>% 
  select(title, year, length, budget, rating, votes) 

movies_romance <- movies %>% 
  filter(movies$Romance == 1) %>% 
  select(title, year, length, budget, rating, votes) 

movies_short <- movies %>% 
  filter(movies$Short == 1) %>% 
  select(title, year, length, budget, rating, votes)
```
